### 2016-04-27 templates/report/research/tex/articles.tex

{% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}

	{% if published_scientific or accepted_scientific %}
\subsubsection{Published or accepted}
\begin{enumerate}
		{% if published_scientific %}
			{% for article in published_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}. {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_scientific %}
			{% for article in accepted_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}. {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
\end{enumerate}
	{% endif %}

	{% if published_dissemin or accepted_dissemin %}
\subsubsection{Published or accepted from the dissemination team}
\begin{enumerate}
		{% if published_dissemin %}
			{% for article in published_dissemin %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}. {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_dissemin %}
			{% for article in accepted_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}. {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
\end{enumerate}
	{% endif %}

	{% if published_tec_trans or accepted_tec_trans %}
\subsubsection{Published or accepted from the technological transfer team}
\begin{enumerate}
		{% if published_tec_trans %}
			{% for article in published_tec_trans %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}. {{ article.article.periodical }},{% endif %}{% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_tec_trans %}
			{% for article in accepted_tec_trans %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}{{ article.article.title }}.{% endif %}{% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{{ article.article.periodical }},{% else %} {{ article.article.authors }}. {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
\end{enumerate}
	{% endif %}

>>>>

{% if published_scientific or accepted_scientific or submitted_scientific or draft_scientific or published_dissemin or accepted_dissemin or submitted_dissemin or draft_dissemin or published_tec_trans or accepted_tec_trans or submitted_tec_trans or draft_tec_trans or published_scientific_in_event or accepted_scientific_in_event or published_dissemin_in_event or accepted_dissemin_in_event or published_tec_trans_in_event or accepted_tec_trans_in_event%}
	{% if published_scientific or accepted_scientific %}
\paragraph{Published or Accepted}
\begin{enumerate}
		{% if published_scientific %}
			{% for article in published_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %}  \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_scientific %}
			{% for article in accepted_scientific %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

	{% if published_dissemin or accepted_dissemin %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Published or accepted from the dissemination team}
		{% if published_dissemin %}
			{% for article in published_dissemin %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_dissemin %}
			{% for article in accepted_dissemin %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

	{% if published_tec_trans or accepted_tec_trans %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Published or accepted from the technological transfer team}
		{% if published_tec_trans %}
			{% for article in published_tec_trans %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {% if article.volume %}\textbf{ {{ article.volume }} }{% endif %}{% if article.number %} ({{ article.number }}),{% endif %}{% if article.start_page and article.end_page %} {{ article.start_page }}-{{ article.end_page }},{% endif %} {% if article.doi %}DOI: {{ article.doi }},{% endif %} {{ article.date|date:"Y" }}.{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_tec_trans %}
			{% for article in accepted_tec_trans %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.periodical }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.periodical }},{% endif %} {{ article.date|date:"Y" }}, to appear.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

	{% if submitted_scientific %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Submitted}
		{% for article in submitted_scientific %}
			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
		{% endfor %}
	{% endif %}

	{% if submitted_dissemin %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Submitted from the dissemination team}
		{% for article in submitted_dissemin %}
			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
		{% endfor %}
	{% endif %}

	{% if submitted_tec_trans %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Submitted from the technological transfer team}
		{% for article in submitted_tec_trans %}
			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
		{% endfor %}
	{% endif %}

	{% if published_scientific_in_event or accepted_scientific_in_event %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Communications in meetings with referee}
		{% if published_scientific_in_event %}
			{% for article in published_scientific_in_event %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_scientific_in_event %}
			{% for article in published_scientific_in_event %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

	{% if published_dissemin_in_event or accepted_dissemin_in_event %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Communications in meetings with referee from the dissemination team}
		{% if published_dissemin_in_event %}
			{% for article in published_dissemin_in_event %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_dissemin_in_event %}
			{% for article in accepted_dissemin_in_event %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

	{% if published_tec_trans_in_event or accepted_tec_trans_in_event %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Communications in meetings with referee from the technological transfer team}
		{% if published_tec_trans_in_event %}
			{% for article in published_tec_trans_in_event %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}.{% endif %}{% endif %}
			{% endfor %}
		{% endif %}
		{% if accepted_tec_trans_in_event %}
			{% for article in accepted_tec_trans_in_event %}
				{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} } {{ article.article.event }},{% else %}\textit{ {{ article.article.authors }}.} {{ article.article.event }},{% endif %}{% if article.article.event.acronym %} {{ article.article.event.acronym }}{% endif %}, {{ article.article.event.local }}, {% if article.article.event.start_date|date:"M" == article.article.event.end_date|date:"M" %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"d, Y" }}, to be held{% else %}{{ article.article.event.start_date|date:"M d" }}-{{ article.article.event.end_date|date:"M d, Y" }}, to be held{% endif %}.{% endif %}
			{% endfor %}
		{% endif %}
	{% endif %}

	{% if draft_scientific %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Drafts}
		{% for article in draft_scientific %}
			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
		{% endfor %}
	{% endif %}

	{% if draft_dissemin %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Drafts from the dissemination team}
		{% for article in draft_dissemin %}
			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
		{% endfor %}
	{% endif %}

	{% if draft_tec_trans %}
\vspace{0.5cm}
\hspace{-1cm}\noindent{\bf Drafts from the technological transfer team}
		{% for article in draft_tec_trans %}
			{% if not article.article.hide %} \item{% if article.article.url %} \textbf{\href{ {{ article.article.url }} }{ {{ article.article.title }}.} }{% else %} \textbf{ {{ article.article.title }} }.{% endif %} {% if article.article.ris_file_authors %}\textit{ {{ article.article.ris_file_authors }} }{% else %}\textit{ {{ article.article.authors }}.}{% endif %}{% endif %}
		{% endfor %}
	{% endif %}
\end{enumerate}
